Autocorrelation of Annual Temperature in Key West, Florida for the 20th Century

### 2020-10-25 Week3/Code/TAutoCorr.tex
CMEECourseWork

\documentclass[12pt]{paper}

@@

\author{Cong Liu}

@@

\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage[colorlinks]{hyperref}

\begin{document}
  \maketitle
  \tableofcontents
  \begin{abstract}
    This paper concerns whether temperatures of years are autocorrelated. Temperatures
    in Key West, Florida for 20th century were used. Lag 1 autocorrelation was tested, and 
    \textit{p}-value was estimated using a simulation approach. The results showed a weak but significant
    correlation between temperature of one year and its successive year.

@@

    \subsection{Estimation of \textit{p}-value}
    A R script is used to estimate \textit{p}-value. To begin with, values of temperature were
    rearranged randomly, and Pearson's correlation coefficient of lag 1 autocorrelation was calculated.
    This process was repeated 10,000 times, and the fraction of correlation coefficients whose absolute 
    values are larger than that from raw data is approximate \textit{p}-value.

@@

  \section{Supplement}
  All codes are wraped in TAutoCorr.R, which is accessible in 
\end{document}

>>>>

\documentclass[12pt]{article}

@@

\author{Cong Liu (cong.liu20@imperial.ac.uk)}

@@

\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage[colorlinks]{hyperref}
\usepackage{hyperref}

\begin{document}
  \maketitle
  \tableofcontents
  \begin{abstract}
    This study concerns whether temperatures of years are autocorrelated. Temperatures
    in Key West, Florida for 20th century were used. Lag 1 autocorrelation was tested, and 
    \textit{p}-value was estimated using a simulation approach. The results showed a weak but significant
    correlation between temperature of one year and its successive year.

@@

    \subsection{Estimation of \texorpdfstring{$\mathit{p}$}{}-value}
    A R script is used to estimate \textit{p}-value. To begin with, values of temperature were
    rearranged randomly, and Pearson's correlation coefficient of lag 1 autocorrelation was calculated.
    This process was repeated 10,000 times, and the fraction of correlation coefficients whose absolute 
    values are larger than that from raw data is approximate \textit{p}-value.

@@

  \section{Supplement}
  All codes are wraped in TAutoCorr.R, which is accessible in 
  \newline
  \href{https://github.com/CongLiu37/CMEECourseWork/tree/main/Week3/Code}{https://github.com/CongLiu37/CMEECourseWork/tree/main/Week3/Code}
\end{document}
